A planetary collision afterglow and transit of the resultant debris cloud

### 2023-10-04 src/tex/ms.tex
[showyourwork] overleaf sync

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

% Begin!
\begin{document}

% Title
\title{An open source scientific article}

% Author list
\author{@mkenworthy}

% Abstract with filler text
\begin{abstract}
    A collision was seen. 
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
Donec vehicula augue eu neque, morbi tristique senectus et netus et.
Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
Phasellus eu tellus sit amet tortor gravida placerat.
Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
Praesent eget sem vel leo ultrices bibendum.
Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
Curabitur auctor semper nulla donec varius orci eget risus.
Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi.
Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae.
Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna.
Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante.
Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient.
Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis.
Pellentesque cursus luctus mauris \citep{Luger2021}.

\bibliography{bib}

\end{document}

>>>>

% Version 1.2 of SN LaTeX, November 2022
%
% See section 11 of the User Manual for version history 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing

%%=======================================================%%
%% to print line numbers in the margin use lineno option %%
%%=======================================================%%

%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style

%%======================================================%%
%% to compile with pdflatex/xelatex use pdflatex option %%
%%======================================================%%

%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style

%%Note: the following reference styles support Namedate and Numbered referencing. By default the style follows the most common style. To switch between the options you can add or remove Numbered in the optional parenthesis. 
%%The option is available for: sn-basic.bst, sn-vancouver.bst, sn-chicago.bst, sn-mathphys.bst. %

\documentclass[sn-nature]{sn-jnl}% Style for submissions to Nature Portfolio journals
%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
%%\documentclass[sn-mathphys,Numbered]{sn-jnl}% Math and Physical Sciences Reference Style
%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
%%\documentclass[sn-vancouver,Numbered]{sn-jnl}% Vancouver Reference Style
%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style 
%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
%%\documentclass[default]{sn-jnl}% Default
%%\documentclass[default,iicol]{sn-jnl}% Default with double column layout

%%%% Standard Packages
%%<additional latex packages if required can be included here>

\usepackage{graphicx}%
\usepackage{multirow}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%  
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
\usepackage{algorithm}%
\usepackage{algorithmicx}%
\usepackage{algpseudocode}%
\usepackage{listings}%
%%%%
%MAK ADDED

\usepackage{etoolbox}

\newcommand*\degr{\ensuremath{^\circ}}
\newcommand*\arcmin{\ensuremath{^\prime}}
\newcommand*\arcsec{\ensuremath{^{\prime\prime}}}

% for bibliography
%\usepackage{natbib}
\def\aap{Astron. \& Astrophys.}
\def\aj{Astron. J.}
\def\apj{Astrophys. J.}
\def\apjs{Astrophys. J. Suppl.}
%\let\apjsupp\apjs
\def\apss{Astrophys. Space Sci.}
\def\araa{Ann. Rev. Astron. Astrophys.}
\def\icarus{Icarus}
\def\mnras{Mon. Not. R. Astron. Soc.}
\def\nat{Nature}
\def\pasp{Proc. Astron. Soc. Pac.}
% Package hyperref Warning: Difference (4) between bookmark levels is greater than one, level fixed on input line 1426.
% 
\setcounter{tocdepth}{1}

\newcommand{\asas}{ASASSN-21qj}
\newcommand{\masyr}{mas~yr$^{-1}$}
\newcommand{\teff}{$T_\mathrm{eff}$}
\newcommand{\rsun}{$R_\odot$}

\begin{document}

%TC:ignore

\title[Planetary collision]{A planetary collision afterglow and transit of the resultant debris cloud}

\author[1]{{\fnm{Matthew} \sur{Kenworthy} }\email{kenworthy@strw.leidenuniv.nl}}
\equalcont{These authors contributed equally to this work.}

\author[2]{{\fnm{Simon} \sur{Lock} }\email{s.lock@bristol.ac.uk}}
\equalcont{These authors contributed equally to this work.}

\author[3,4]{{\fnm{Grant} \sur{Kennedy} }\email{G.Kennedy@warwick.ac.uk}}
\equalcont{These authors contributed equally to this work.}

\author[1]{{\fnm{Richelle} \sur{van Capelleveen} }\email{capelleveen@strw.leidenuniv.nl}}
\equalcont{These authors contributed equally to this work.}

\author[5]{{\fnm{Eric} \sur{Mamajek} }\email{Eric.Mamajek@jpl.nasa.gov}}
\equalcont{These authors contributed equally to this work.}

\author[6]{{\fnm{Ludmila} \sur{Carone} }\email{ludmila.carone@oeaw.ac.at}}
\equalcont{These authors contributed equally to this work.}

\author[7,8,9]{{\fnm{Franz-Josef} \sur{Hambsch} }\email{hambsch@telenet.be}}

\author[10]{{\fnm{Joseph} \sur{Masiero} }\email{jmasiero@ipac.caltech.edu}}

\author[11]{{\fnm{Amy} \sur{Mainzer} }\email{amainzer@arizona.edu}}

\author[10]{{\fnm{J. Davy} \sur{Kirkpatrick} }\email{davy@ipac.caltech.edu}}

\author[12,13]{{\fnm{Edward} \sur{Gomez} }\email{egomez@lco.global}}

\author[14]{{\fnm{Zo{\"e}} \sur{Leinhardt} }\email{Zoe.Leinhardt@bristol.ac.uk}}

\author[14]{{\fnm{Jingyao} \sur{Dou} }\email{qb20321@bristol.ac.uk}}

\author[15]{{\fnm{Pavan} \sur{Tanna} }\email{pt426@cam.ac.uk}}

\author[16]{{\fnm{Arttu} \sur{Sainio} }\email{arttu.sainio@elisanet.fi}}

\author[17]{{\fnm{Hamish} \sur{Barker} }\email{hamish.barker@gmail.com}}

\author[18]{{\fnm{St\'{e}phane} \sur{Charbonnel} }\email{stephane.charbonnel@2spot.org}}

\author[18]{{\fnm{Olivier} \sur{Garde} }\email{olivier.garde@2spot.org}}

\author[18]{{\fnm{Pascal} \sur{Le D\^{u}} }\email{pascal.ledu@2spot.org}}

\author[18]{{\fnm{Lionel} \sur{Mulato} }\email{lionel.mulato@2spot.org}}

\author[18]{{\fnm{Thomas} \sur{Petit} }\email{thomas.petit@2spot.org}}

\author[19]{{\fnm{Michael} \sur{Rizzo Smith} }\email{rizzosmith.1@osu.edu}}

\affil[1]{\orgdiv{Leiden Observatory}, \orgname{Leiden University}, \orgaddress{\street{P.O. Box 9513}, \city{Leiden}, \postcode{2300 RA}, \country{The Netherlands}}}

\affil[2]{\orgdiv{School of Earth Sciences}, \orgname{University of Bristol}, \orgaddress{\street{Queens Road}, \city{Bristol}, \postcode{BS8 1QU}, \country{UK}}}

\affil[3]{\orgdiv{Department of Physics}, \orgname{University of Warwick}, \orgaddress{\street{Gibbet Hill Road}, \city{Coventry}, \postcode{CV4 7AL}, \country{UK}}}

\affil[4]{\orgdiv{Centre for Exoplanets}, \orgname{University of Warwick}, \orgaddress{\street{Gibbet Hill Road}, \city{Coventry}, \postcode{CV4 7AL}, \country{UK}}}

\affil[5]{\orgdiv{Jet Propulsion Laboratory}, \orgname{California Institute of Technology}, \orgaddress{\street{4800 Oak Grove Drive}, \city{Pasadena}, \postcode{91109}, \state{CA}, \country{USA}}}

\affil[6]{\orgdiv{Space Research Insitute}, \orgname{Austrian Academy of Sciences}, \orgaddress{\street{Schmiedlstrasse 6}, \city{Graz}, \postcode{A-8042}, \country{Austria}}}

\affil[7]{\orgname{Vereniging Voor Sterrenkunde}, \orgaddress{\street{Oostmeers 122 C}, \city{Bruges}, \postcode{8000 Brugge}, \country{Belgium}}}

\affil[8]{\orgname{American Association of Variable Star Observers}, \orgaddress{\street{185 Alewife Brook Parkway}, \city{Cambridge}, \postcode{MA 02138}, \state{MA}, \country{USA}}}

\affil[9]{\orgname{Bundesdeutsche Arbeitsgemeinschaft f{\"u}r Ver{\"a}nderliche Sterne e. V.}, \orgaddress{\street{Munsterdamm 90}, \city{Berlin}, \postcode{D-12169}, \country{Germany}}}

\affil[10]{\orgdiv{IPAC}, \orgname{Caltech}, \orgaddress{\street{1200 E California Blvd}, \city{Pasadena}, \postcode{MC 100-22}, \state{CA}, \country{USA}}}

\affil[11]{\orgdiv{Lunar and Planetary Laboratory}, \orgname{University of Arizona}, \orgaddress{\street{1629 E. University Blvd.}, \city{Tucson}, \postcode{85721}, \state{AZ}, \country{USA}}}

\affil[12]{\orgdiv{Las Cumbres Observatory}, \orgaddress{\street{6740 Cortona Dr}, \city{Goleta}, \postcode{93117}, \state{CA}, \country{USA}}}

\affil[13]{\orgdiv{School of Physics and Astronomy}, \orgname{Cardiff University}, \orgaddress{\street{The Parade}, \city{Cardiff}, \postcode{CF24 3AA}, \country{UK}}}

\affil[14]{\orgdiv{School of Physics, H H Wills Physics Laboratory}, \orgname{University of Bristol}, \orgaddress{\street{Tyndall Avenue}, \city{Bristol}, \postcode{BS8 1TL}, \country{USA}}}

\affil[15]{\orgdiv{Institute of Astronomy}, \orgname{University of Cambridge}, \orgaddress{\street{Madingley Road}, \city{Cambridge }, \postcode{CB3 0HA}, \country{UK}}}

\affil[16]{\orgname{Independent researcher}, \orgaddress{\street{J{\"a}rvipuistonkatu 7 A 10}, \city{J{\"a}rvenp{\"a}{\"a}}, \postcode{04430}, \country{Finland}}}

\affil[17]{\orgname{Variable Stars South}, \orgaddress{\street{Rutherford Street}, \city{Nelson}, \country{New Zealand}}}

\affil[18]{\orgname{Southern Spectrocopic Project Observatory Team}, \orgaddress{\street{45, Chemin du lac}, \city{Chabons}, \postcode{38690}, \country{FRANCE}}}

\affil[19]{\orgdiv{Department of Astronomy}, \orgname{The Ohio State University}, \orgaddress{\street{140 West 18th Avenue}, \city{Columbus}, \postcode{43210}, \state{OH}, \country{USA}}}

\abstract{
Planets grow in rotating disks of dust and gas around forming stars, some of which can subsequently collide in giant impacts after the gas component is removed from the disk \cite{Williams11,Wyatt15,Hughes18}.
%
Monitoring programs with the warm Spitzer mission have recorded significant and rapid changes in mid-infrared output for several stars, interpreted as variations in the surface area of warm dusty material ejected by planetary-scale collisions and heated by the central star: e.g., NGC 2354–ID8 \cite{2014Sci...345.1032M,Su19}, HD 166191 \cite{Su22} and V844 Persei \cite{2021ApJ...918...71R}.
%
%However, observational constraints on the aftermath and frequency of such impacts are difficult to obtain.
%
Here we report combined observations of the young ($\sim$~300~Myr), solar-like star \asas{}: an infrared brightening consistent with a blackbody temperature of 1000 K and a luminosity of 4\% of that of the star lasting for about 1000\,days, partially overlapping in time with a complex and deep wavelength-dependent optical eclipse that lasted for about 500 days.
%
The optical eclipse started 2.5\,years after the infrared brightening, implying an orbital period of at least that duration.
%
These observations are consistent with a collision between two exoplanets of several to tens of Earth masses at 2-16\,au from the central star. 
%
Such an impact produces a hot, highly-extended post-impact remnant with sufficient luminosity to explain the infrared observations.
%
Transit of the impact debris, sheared by orbital motion into a long cloud, causes the subsequent complex eclipse of the host star.
}

\keywords{exoplanets, planet formation, debris disks}
%TC:endignore

\maketitle

% ███╗░░░███╗░█████╗░██╗███╗░░██╗  ░█████╗░██████╗░████████╗██╗░█████╗░██╗░░░░░███████╗
% ████╗░████║██╔══██╗██║████╗░██║  ██╔══██╗██╔══██╗╚══██╔══╝██║██╔══██╗██║░░░░░██╔════╝
% ██╔████╔██║███████║██║██╔██╗██║  ███████║██████╔╝░░░██║░░░██║██║░░╚═╝██║░░░░░█████╗░░
% ██║╚██╔╝██║██╔══██║██║██║╚████║  ██╔══██║██╔══██╗░░░██║░░░██║██║░░██╗██║░░░░░██╔══╝░░
% ██║░╚═╝░██║██║░░██║██║██║░╚███║  ██║░░██║██║░░██║░░░██║░░░██║╚█████╔╝███████╗███████╗
% ╚═╝░░░░░╚═╝╚═╝░░╚═╝╚═╝╚═╝░░╚══╝  ╚═╝░░╚═╝╚═╝░░╚═╝░░░╚═╝░░░╚═╝░╚════╝░╚══════╝╚══════╝

\section{Main Article}\label{sec1}

% 262 words

% ▀█▀ █░█ █▀▀   █▀▀ █░█ █▀▀ █▄░█ ▀█▀
% ░█░ █▀█ ██▄   ██▄ ▀▄▀ ██▄ █░▀█ ░█░

The otherwise unremarkable star 2MASS J08152329-3859234 underwent a sudden optical dimming event in December 2021 \cite{RizzoSmith21,RizzoSmith22} and was assigned the identifier \asas{} by the ASAS-SN survey \citep{shappee_man_2014,kochanek_all-sky_2017}.
%
Here, we combine both optical (from the Las Cumbres Observatory Global Telescope, LCOGT) and infrared (from the WISE satellite) observations of \asas~for the years before and after this dimming event (Figure~\ref{fig:wisephot}). 
%
Optical multiband photometry shows a wavelength dependent depth consistent with extinction by sub-micron particles.
%
About 900 days prior to the optical dimming event, the \asas~system showed a significant brightening in the infrared, of 0.4 magnitudes at 3.8 microns ($W1$) and 0.8 magnitudes at 4.5 microns ($W2$).
%
Before this time the IR brightness was consistent with being purely stellar.
%
The increased IR fluxes indicate that in addition to the quiescent stellar flux, there was new emission at a temperature of approximately 1000\,K.
%
Such a remarkable combination of observations, particularly the 2.5\,year delay between the IR and optical variation, requires an explanation.

% █ █▀█   █▀▄ █░█ █▀ ▀█▀   █░░ █▀█ █▀▀ ▄▀█ ▀█▀ █ █▀█ █▄░█
% █ █▀▄   █▄▀ █▄█ ▄█ ░█░   █▄▄ █▄█ █▄▄ █▀█ ░█░ █ █▄█ █░▀█

% █▀█ █▀█ ▀█▀ █ █▀▀ ▄▀█ █░░   ▄▀█ █▄░█ █▀▄   █ █▀█   █▀▀ █░█ █▀█ █░█ █▀▀ █▀
% █▄█ █▀▀ ░█░ █ █▄▄ █▀█ █▄▄   █▀█ █░▀█ █▄▀   █ █▀▄   █▄▄ █▄█ █▀▄ ▀▄▀ ██▄ ▄█

The optical and infrared light curves (Figure \ref{fig:wisephot}) provide key constraints on any proposed scenario.
%
The post-brightening IR fluxes in the $W1$ and $W2$ WISE passbands are consistent with emission at a blackbody temperature of $1000 \pm 100$\,K and this temperature is sustained, within error, for the remainder of our observation window, despite a decline in the total flux.
%
For an emitter located at the distance of ASASSN-21qj from Earth, and the observed  maximum luminosity of approximately 0.04\,$L_\star$, this implies an emitting area of 0.01\,au$^2$, equivalent to an object with a radius of 7\,$R_\odot$, or $750$\,$R_{\rm Earth}$.
%
If this emission was from material -- e.g., dust -- passively heated by proximity to the star, then that material must have been generated and remained within about 0.1\,au to produce the observed temperature.

% █▀█ █░░ ▄▀█ █▄░█ █▀▀ ▀█▀   █▀▀ █▀█ █░░ █░░ █ █▀ █ █▀█ █▄░█
% █▀▀ █▄▄ █▀█ █░▀█ ██▄ ░█░   █▄▄ █▄█ █▄▄ █▄▄ █ ▄█ █ █▄█ █░▀█

One possible explanation is that we are observing two unrelated but coincidental phenomena: a warm dust generating collision within 0.1 au of the star, with a separate object transiting the star 900 days later.
%
Two events that are themselves very rare occurring independently in one system is, however, highly improbable.
%
A second explanation is that warm dust is generated close to the star and causes the optical transit, but this requires a fine-tuned configuration where the star is optically blocked by scale height variations in the resulting disk.

Instead, we hypothesize that are we are observing the aftermath of a single collision between super-Earths or mini Neptunes -- a so-called giant impact -- between 2 and 16\,au from the star. 
%
These distances are determined, respectively, by the delay between the IR brightening and the optical eclipse (Fig. \ref{fig:wisephot}), and by gradients in the optical light curve (Fig. \ref{fig:eclipse_overview}).
%
In contrast to other extreme debris disk events where the star heats the dust, we propose that the infrared emission is directly from the post-impact body \cite{Lock2017,2009ApJ...704..770M}, and that impact debris produced the optical transit.
%
Giant impacts are a common occurrence in planet formation \cite{Schlichting2018a,DAngelo2018} and also occur during instabilities in older systems \cite{Kaib2016}; this would explain the observations with a single event of a type that are expected for systems with ages like \asas{}.

Giant impacts are one of the most energetic events planets experience.
%
For example, the kinetic energy of impacts between two half-Neptune-mass bodies range from $10^{33}$ to $10^{34}$~J, enough to vaporize the colliding bodies several times over.
%
A large fraction of this energy is dissipated in the colliding bodies and post-impact bodies are substantially melted and vaporized \cite{Nakajima2015,Lock2017,Carter2020}.
%
Furthermore, extreme torques exerted in impacts often produce rapidly rotating bodies \cite{Lock2017}.
%
Such low density and rotationally-flattened bodies can be hundreds of times larger than the pre-impact planets \cite{Lock2017} with correspondingly large radiative surfaces.

% 205 words

Giant impacts produce significant amounts of debris, typically around 1\% of the colliding mass, that is injected into orbit around the host star\cite{Canup2001,Lock18}.
%
Impact ejecta has a wide range of sizes, from sub-micron dust to planetesimals of tens to hundreds of kilometers, and often contains the most highly heated material \cite{Benz2008_Mercury_book,Leinhardt2015,Carter2020a}.
%
For sufficiently high impact velocities ($>1$~km~s$^{-1}$ for water ice, and $>8$~km~s$^{-1}$ for forsterite) a substantial fraction of this material is vaporised \cite{Stewart2008,Davies2020,Carter2020a}.
%
Shearing of droplets and cooling and condensation of vapor produces a population of small dust grains and solid spherules.
%
The size distribution of this fraction of the debris is uncertain, due to difficulties in modelling condensate nucleation and breakup, but previous work suggests that debris could range in size from sub-micron to decimeters \cite{Benz2008_Mercury_book,Johnson2015}.
%
The wavelength-dependent eclipse suggests that the optical depth of the transiting dust cloud is dominated by sub-micron grains, consistent with these previous estimates.
%
While the fading of the excess infrared flux occurs within 100 days of the start of the optical transit, we consider the timing to be coincidental because there is no clear correspondence between the light curves, for example no  change in the (six month cadence) IR flux when the star dims in the optical wavelengths just before MJD 59500.

% 200 words

% █▀█ █▀▀ █▀▄▀█ █▄░█ ▄▀█ █▄░█ ▀█▀   █▀ █ ▀█ █▀▀
% █▀▄ ██▄ █░▀░█ █░▀█ █▀█ █░▀█ ░█░   ▄█ █ █▄ ██▄

The radiative flux from post-impact bodies has not been explored in depth.
%
Computational resource limitations make resolving the low-density outer regions and photosphere of post-impact bodies extremely challenging.
%
However, preliminary simulations of impacts between super-Earth and mini-Neptunes place an approximate lower limit on the extent of post-impact bodies and show that post-impact bodies can extend to hundreds of Earth radii.
%
Such an object radiating at $\sim$1000~K would produce a flux comparable to the 0.04~$L_*$ inferred from our observations.

Independent of impact simulations, there are fundamental limits on the size of post-impact bodies from the Hill and Bondi radii.
%
Any post-impact structure must lie within the Hill sphere, the distance within which the gravity of an object dominates over that of the star.
%
Furthermore, only vapor within the Bondi radius would be bound to the post-impact body.
%
Figure~\ref{fig:Hill_Bondi_R}A shows the Hill radii at different distances from ASASSN-21qj (solid lines) and the Bondi radius for example gas species (dotted lines).
%
Beyond 2.4\,au, the Hill radii of greater than Earth-mass bodies are large enough to accommodate a post-impact body capable of producing the required IR flux ($\sim7R_*$, dotted line). 
%
Heavier gases (H$_2$O, SiO, and SiO$_2$) are also bound to bodies of more than a few Earth masses.
%
A post-impact body of a few Earth masses can hence theoretically produce the observed IR emission, with a photosphere that is dust and/or vapor.

% █░█░█ ▄▀█ ▀█▀ █▀▀ █▀█   ▄▀█ █▀   █▀▀ █▀█ █▀█ █░░ ▄▀█ █▄░█ ▀█▀
% ▀▄▀▄▀ █▀█ ░█░ ██▄ █▀▄   █▀█ ▄█   █▄▄ █▄█ █▄█ █▄▄ █▀█ █░▀█ ░█░

A key line of evidence for direct detection of a post-impact body is the constant emission temperature.
%
It is argued \cite{Lock18} that rocky post-impact bodies become optically thin at low pressures where radiative loss drives rapid condensation of the rock vapor.
%
The emission temperature is then set by the liquid-vapor phase boundary and is constant until the post-impact body almost fully condenses \cite{Lock18,Caracas2023}.
%
The dew point (onset of condensation) and bubble point (onset of substantial vaporization) of material with bulk silicate Earth composition are similar \cite[$\sim2300$~K, within $\sim 100$~K;][]{Lock18,Fegley2023_BSE_cond} at the low pressures of the photosphere of a post-impact body.
%
However, even small amounts of water (10$^{-3}$ mole fraction) may lower the bubble and dew points for silicates by $\sim$100~K \cite[][]{Fegley2023_BSE_cond,Lock18}. 
%
The emission temperature of bodies produced by collisions of proto-planets composed of rock and ices/volatiles could be buffered at $\sim$1000~K during early evolution.

% 284 words

% ▀█▀ █ █▀▄▀█ █▀▀   █▀▄ █▀▀ █▀▀ ▄▀█ █▄█
% ░█░ █ █░▀░█ ██▄   █▄▀ ██▄ █▄▄ █▀█ ░█░

The temporal variation of flux from a post-impact body is controlled by evolution of the bodies' size which is governed by a number of competing factors \cite{Lock2018moon,Lock2020}, including radiative energy loss, viscous spreading, and mass and angular momentum transfer by condensates.
%
For silicate-dominated post-impact bodies, the high emission temperature means that radiative cooling dominates, and the post-impact body contracts rapidly, fully condensing over years to thousands of years \cite{Lock2018moon,Lock2020}.
%
The body we observed has a much lower emission temperature, and contracted substantially more slowly.
%
Figure~\ref{fig:Hill_Bondi_R}~B and C show evolution of conceptual post-impact bodies in the limiting case that radiative cooling dominates.
%
If sufficient mass is injected into the outer regions (i.e., less negative power law exponents) the observed flux can remain constant for an initial period and then decays over the order of hundreds of days, in agreement with infrared observations.
%
Further work is required to understand the structure and evolution of bodies produced by impacts between super-Earths and mini-Neptunes of different compositions and identify temporal flux variations consistent with our observations.

\clearpage

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\burl{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}
\providecommand{\doi}[1]{\url{https://doi.org/#1}}
\bibcommenthead

\bibitem{Williams11}
\bibinfo{author}{{Williams}, J.~P.} \& \bibinfo{author}{{Cieza}, L.~A.}
\newblock \bibinfo{title}{{Protoplanetary Disks and Their Evolution}}.
\newblock \emph{\bibinfo{journal}{\araa}} \textbf{\bibinfo{volume}{49}},
  \bibinfo{pages}{67--117} (\bibinfo{year}{2011}).
\newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2011ARA%26A..49...67W}.

\bibitem{Wyatt15}
\bibinfo{author}{{Wyatt}, M.~C.}, \bibinfo{author}{{Pani{\'c}}, O.},
  \bibinfo{author}{{Kennedy}, G.~M.} \& \bibinfo{author}{{Matr{\`a}}, L.}
\newblock \bibinfo{title}{{Five steps in the evolution from protoplanetary to
  debris disk}}.
\newblock \emph{\bibinfo{journal}{\apss}} \textbf{\bibinfo{volume}{357}},
  \bibinfo{pages}{103} (\bibinfo{year}{2015}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2015Ap&SS.357..103W}.

\bibitem{Hughes18}
\bibinfo{author}{{Hughes}, A.~M.}, \bibinfo{author}{{Duch{\^e}ne}, G.} \&
  \bibinfo{author}{{Matthews}, B.~C.}
\newblock \bibinfo{title}{{Debris Disks: Structure, Composition, and
  Variability}}.
\newblock \emph{\bibinfo{journal}{\araa}} \textbf{\bibinfo{volume}{56}},
  \bibinfo{pages}{541--591} (\bibinfo{year}{2018}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2018ARA&A..56..541H}.

\bibitem{2014Sci...345.1032M}
\bibinfo{author}{{Meng}, H. Y.~A.} \emph{et~al.}
\newblock \bibinfo{title}{{Large impacts around a solar-analog star in the era
  of terrestrial planet formation}}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{345}},
  \bibinfo{pages}{1032--1035} (\bibinfo{year}{2014}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2014Sci...345.1032M}.

\bibitem{Su19}
\bibinfo{author}{{Su}, K. Y.~L.} \emph{et~al.}
\newblock \bibinfo{title}{{Extreme Debris Disk Variability: Exploring the
  Diverse Outcomes of Large Asteroid Impacts During the Era of Terrestrial
  Planet Formation}}.
\newblock \emph{\bibinfo{journal}{\aj}} \textbf{\bibinfo{volume}{157}},
  \bibinfo{pages}{202} (\bibinfo{year}{2019}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2019AJ....157..202S}.

\bibitem{Su22}
\bibinfo{author}{{Su}, K. Y.~L.}, \bibinfo{author}{{Kennedy}, G.~M.},
  \bibinfo{author}{{Schlawin}, E.}, \bibinfo{author}{{Jackson}, A.~P.} \&
  \bibinfo{author}{{Rieke}, G.~H.}
\newblock \bibinfo{title}{{A Star-sized Impact-produced Dust Clump in the
  Terrestrial Zone of the HD 166191 System}}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{927}},
  \bibinfo{pages}{135} (\bibinfo{year}{2022}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2022ApJ...927..135S}.

\bibitem{2021ApJ...918...71R}
\bibinfo{author}{{Rieke}, G.~H.}, \bibinfo{author}{{Su}, K.~Y.~L.},
  \bibinfo{author}{{Melis}, C.} \& \bibinfo{author}{{G{\'a}sp{\'a}r}, A.}
\newblock \bibinfo{title}{{Extreme Variability of the V488 Persei Debris
  Disk}}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{918}},
  \bibinfo{pages}{71} (\bibinfo{year}{2021}).

\bibitem{RizzoSmith21}
\bibinfo{author}{{Rizzo Smith}, M.} \emph{et~al.}
\newblock \bibinfo{title}{{ASASSN-21qj: A Rapidly Fading, Sun-Like Star}}.
\newblock \emph{\bibinfo{journal}{The Astronomer's Telegram}}
  \textbf{\bibinfo{volume}{14879}}, \bibinfo{pages}{1} (\bibinfo{year}{2021}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2021ATel14879....1R}.

\bibitem{RizzoSmith22}
\bibinfo{author}{{Rizzo Smith}, M.} \emph{et~al.}
\newblock \bibinfo{title}{{An Update on ASASSN-21qj: A Rapidly Fading, Sun-Like
  Star; Back With a Vengeance}}.
\newblock \emph{\bibinfo{journal}{The Astronomer's Telegram}}
  \textbf{\bibinfo{volume}{15531}}, \bibinfo{pages}{1} (\bibinfo{year}{2022}).
\newblock
  \urlprefix\url{https://ui.adsabs.harvard.edu/abs/2022ATel15531....1R}.

\bibitem{shappee_man_2014}
\bibinfo{author}{Shappee, B.~J.} \emph{et~al.}
\newblock \bibinfo{title}{The {Man} behind the {Curtain}: {X}-{Rays} {Drive}
  the {UV} through {NIR} {Variability} in the 2013 {Active} {Galactic}
  {Nucleus} {Outburst} in {NGC} 2617}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{788}},
  \bibinfo{pages}{48} (\bibinfo{year}{2014}).
\newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2014ApJ...788...48S}.

\bibitem{kochanek_all-sky_2017}
\bibinfo{author}{Kochanek, C.~S.} \emph{et~al.}
\newblock \bibinfo{title}{The {All}-{Sky} {Automated} {Survey} for {Supernovae}
  ({ASAS}-{SN}) {Light} {Curve} {Server} v1.0}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{129}}, \bibinfo{pages}{104502}
  (\bibinfo{year}{2017}).
\newblock \urlprefix\url{http://adsabs.harvard.edu/abs/2017PASP..129j4502K}.

\bibitem{Lock2017}
\bibinfo{author}{Lock, S.~J.} \& \bibinfo{author}{Stewart, S.~T.}
\newblock \bibinfo{title}{The structure of terrestrial bodies: {Impact}
  heating, corotation limits, and synestias}.
\newblock \emph{\bibinfo{journal}{Journal of Geophysical Research: Planets}}
  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{950--982}
  (\bibinfo{year}{2017}).
\newblock \urlprefix\url{http://doi.wiley.com/10.1002/2016JE005239}.

\bibitem{2009ApJ...704..770M}
\bibinfo{author}{{Miller-Ricci}, E.}, \bibinfo{author}{{Meyer}, M.~R.},
  \bibinfo{author}{{Seager}, S.} \& \bibinfo{author}{{Elkins-Tanton}, L.}
\newblock \bibinfo{title}{{On the Emergent Spectra of Hot Protoplanet Collision
  Afterglows}}.
\newblock \emph{\bibinfo{journal}{\apj}} \textbf{\bibinfo{volume}{704}},
  \bibinfo{pages}{770--780} (\bibinfo{year}{2009}).

\bibitem{Schlichting2018a}
\bibinfo{author}{Schlichting, H.~E.}
\newblock \bibinfo{title}{ in \textit{Formation of super-{Earths}}} (eds
  \bibinfo{editor}{Hans, D.} \& \bibinfo{editor}{Belmonte, J.~A.})
  \emph{\bibinfo{booktitle}{Handbook of {Exoplanets}}}
  (\bibinfo{publisher}{Springer}, \bibinfo{year}{2018}).
\newblock \urlprefix\url{http://arxiv.org/abs/1802.03090}.
\newblock \bibinfo{note}{ArXiv: 1802.03090}.

\bibitem{DAngelo2018}
\bibinfo{author}{D’Angelo, G.} \& \bibinfo{author}{Lissauer, J.~J.}
\newblock \bibinfo{title}{ in \textit{Formation of {Giant} {Planets}}} (eds
  \bibinfo{editor}{Deeg, H.~J.} \& \bibinfo{editor}{Belmonte, J.~A.})
  \emph{\bibinfo{booktitle}{Handbook of {Exoplanets}}} \bibinfo{pages}{1--25}
  (\bibinfo{publisher}{Springer International Publishing},
  \bibinfo{address}{Cham}, \bibinfo{year}{2018}).
\newblock \urlprefix\url{https://doi.org/10.1007/978-3-319-30648-3_140-2}.
